Reviewer comments from PeerJ

### 2015-02-20 PeerJResponse.tex
Edits
questions for you two with respect to the density stuff from Doebley
and Lukens as it compares to our design

@@

\lev{I have no strong feelings about this.}
\mbh{fine with me to move to supplement}

@@

\lev{Okay we can maybe take these statements out? It would seem that none of the reviewers have ever been happy with what we have had to say with respect to mex vs parv, or unequal sampling. we have discussed why sampling is unequal and why there was no phenotyping for mex.}

\mbh{my vote would be to remove the comparisons between \emph{parv} and \emph{mex} but to still note the high frequency in Jalisco}
\jri{ok either way here}
\lev{I vote remove since everyone has seemed unhappy with this}

>>>>

\lev{So I have checked this. Their experimental design was with maize (don't know if that matters) but in low density plants were placed 36'' apart within rows and rows were 30'' apart. In the high density design plants were 12'' apart within rows and 30'' apart between rows. On each side of the row for the high density Helianthus annus was palnted 12'' away from seedlings to provide extra canopy cover.}

\lev{My guess is that later on our plants were crowded, but early on in the measurements they should not have been shading each other, and tillering then would not have been affected in the early measurements. What do you guys think?}

@@

\res{We appreciate your suggestion but have decided to leave Figure 3 in the main text, as we feel it provides a nice visual representation for the numbers and take home message presented from the STRUCTURE analysis.}

@@

\res{We have removed the comparisons made about the difference in frequencies of the \emph{Hopscotch} allele between ssp. \emph{parviglumis} and ssp. \emph{mexicana}.}
